Grip strength, mating success, and immune and energy costs in a population sample of US women and men: a registered report

### 2024-06-07 paper.qmd
Combining pilot and confirmatory plots, part I

plot_immune <- forestplot(
  immune_models$mwbc,
  immune_models$mwbc_alt,
  intercept = F,
  facet = F,
  dodgewidth = .4,
  varnames = vnames, 
  modelnames = mmnames) +
  scale_color_binary() +
  theme_minimal(17) +
  guides(colour = guide_legend(reverse = T), shape = guide_legend(reverse = T))

ggsave("Figures/plot_immune.pdf", plot_immune, width = 14, height = 7)

plot_immune
```

@@

plot_energy <- forestplot(
  intake_models$m_energy,
  intake_models$m_energy_alt,
  intercept = F,
  facet = F,
  dodgewidth = .4,
  varnames = vnames, 
  modelnames = mmnames) +
  scale_color_binary() +
  ggtitle('Energy') +
  theme_bw(17) +
  guides(colour = guide_none(), shape = guide_none())

plot_protein <- forestplot(
  intake_models$m_protein,
  intake_models$m_protein_alt,
  intercept = F,
  facet = F,
  dodgewidth = .4,
  varnames = vnames, 
  modelnames = mmnames) +
  scale_color_binary() +
  guides(colour = guide_legend(reverse = T), shape = guide_legend(reverse = T)) +
  ggtitle('Protein') +
  theme_bw(17) +
  theme(axis.text.y = element_blank())

>>>>

plot_immune_both <- 
  plot_immune + guides(colour = 'none', shape = 'none') + plot_immune_stage2 + plot_layout(axes = 'collect', guides = 'collect')

ggsave("Figures/plot_immune_both.pdf", plot_immune, width = 14, height = 7)

plot_immune_both
```

@@

plot_energy <- forestplot(
  intake_models$m_energy,
  intake_models$m_energy_alt,
  intercept = F,
  facet = F,
  dodgewidth = .4,
  varnames = vnames, 
  modelnames = mmnames) +
  scale_color_binary() +
  ggtitle('Stage 1: Pilot Energy') +
  theme_bw(17) +
  guides(colour = guide_none(), shape = guide_none())

plot_protein <- forestplot(
  intake_models$m_protein,
  intake_models$m_protein_alt,
  intercept = F,
  facet = F,
  dodgewidth = .4,
  varnames = vnames, 
  modelnames = mmnames) +
  scale_color_binary() +
  guides(colour = guide_legend(reverse = T), shape = guide_legend(reverse = T)) +
  ggtitle('Stage 1: Pilot Protein') +
  theme_bw(17) +
  theme(axis.text.y = element_blank())
